---
title: "Homework 4"
author: "Gage Clawson, Juan Silva"
date: "5/31/2019"
output:
  html_document: default
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(janitor)
library(stargazer)
```

```{r, include=FALSE}
#read in data
carbon <- read_csv("HW4Data.csv") %>%
  clean_names()
```

1. Write down a plausible functional form for the marginal cost of abatement for sector A. Use regression analysis to estimate the parameters of that function. Repeating this for sectors B, C, and D will give you a model of the marginal cost of abatement function for each sector. How well do your models fit the data for each sector? You may need to experiment with different functional forms. Produce a plot of the estimated marginal abatement cost functions in all four sectors (this plot should go in your memo).

```{r, include = FALSE}
carbon_tidy <- gather(carbon, sector, mc, mc_a:mc_d) %>%
  mutate(sector = case_when(
    sector == "mc_a" ~ "Sector A",
    sector == "mc_b" ~ "Sector B",
    sector == "mc_c" ~ "Sector C",
    sector == "mc_d" ~ "Sector D"
  ))

#use regression to define functions for marginal cost of abatement
lm_a <- lm(data = carbon, mc_a ~ abatement) 
summary(lm_a)
# mc_a = -8.64448 + 0.57684*abatement

lm_b <- lm(data = carbon, mc_b ~ abatement) 
summary(lm_b)
# mc_b = 9.31770 + 0.19874*abatement

lm_c <- lm(data = carbon, mc_c ~ abatement) 
summary(lm_c)
# mc_c = -11.65503 + 0.78383*abatement

lm_d <- lm(data = carbon, mc_d ~ abatement) 
summary(lm_d)
# mc_d = 9.68751 + 0.25993*abatement

#save all slopes and intercepts 
slope_a <- lm_a$coefficients[2]
slope_b <- lm_b$coefficients[2]
slope_c <- lm_c$coefficients[2]
slope_d <- lm_d$coefficients[2]

intercept_a <- lm_a$coefficients[1]
intercept_b <- lm_b$coefficients[1]
intercept_c <- lm_c$coefficients[1]
intercept_d <- lm_d$coefficients[1]

```


```{r, echo = FALSE}
stargazer(lm_a, lm_b, lm_c, lm_d, type="text", title="Table 1: Regression Results")
```


```{r, echo = FALSE}
## plot all the data and corresponding regression lines. ggplot one is better IMO
ggplot(data = carbon_tidy, aes(x=abatement, y = mc)) + geom_point() +
  geom_smooth(method="lm", se = FALSE) +
  facet_wrap(~sector, scales = "free") +
  theme_bw() +
  labs(x = "Abatement (tons)", y = "Marginal Cost", title = "Estimated Marginal Abatement Cost Functions") 


```

Marginal Cost of Abatement Functions: 
$$MC_A= -8.65 + 0.58(Abatement)$$
$$MC_B= 9.32 + 0.2 (Abatement)$$
$$MC_C = -11.66 + 0.78 (Abatement)$$
$$MC_D = 9.69 + 0.26 (Abatement)$$

2. Using these models and the current level of carbon emissions, derive each sector’s demand curve for carbon emissions. In other words, how much would each sector be willing to pay for the right to pollute the first unit, second unit, etc? Draw these demand curves on a graph. Which sector is willing to pay the most for the first unit of carbon emissions?

```{r, include = FALSE}
#lets make dataframe columns for abatement, carbon emissions A, MB_A, carbon emissions B, MB_B, carbon emissions C, MB_C, carbon emissions D, MB_D

abatement <- seq(0,300,10)

#current emissions 180, meaning a point will be (0,180) for sector a. Make a list from 0 to 180 by 10 
emissions_A <- seq(180,0, -10)

marg_benefit <- merge(abatement, emissions_A, by = "row.names", all = TRUE) %>%
  select(-Row.names) %>%
  rename(abatement = x, emissions_A = y) %>%
  arrange(abatement)

emissions_B <- seq(200, 0, -10)

marg_benefit <- merge(marg_benefit, emissions_B, by = "row.names", all = TRUE) %>%
  select(-Row.names) %>%
  rename(emissions_B = y) %>%
  arrange(abatement)

emissions_C <- seq(220, 0 , -10)
  
marg_benefit <- merge(marg_benefit, emissions_C, by = "row.names", all = TRUE) %>%
  select(-Row.names) %>%
  rename(emissions_C = y) %>%
  arrange(abatement)

emissions_D <- seq(300, 0 , -10)

marg_benefit <- merge(marg_benefit, emissions_D, by = "row.names", all = TRUE) %>%
  select(-Row.names) %>%
  rename(emissions_D = y) %>%
  arrange(abatement)

#make the demand function for a 

demand_A_fn <- function(x){
  slope_a*(x) + intercept_a #180 is the x intercept, has the same slope because it is just the inverse 
}

#evalute demand function at each value for emissions_A
abatement_A <- seq(0,180, 10)
demand_A <- demand_A_fn(abatement_A) 

marg_benefit <- merge(marg_benefit, demand_A, by = "row.names", all = TRUE) %>%
  select(-Row.names) %>%
  rename(demand_A = y) %>%
  arrange(abatement)


#95.2 is the y intercept 

demand_B_fn <- function(x){
  slope_b*(x) + intercept_b
}

abatement_B <- seq(0,200,10)
demand_B <- demand_B_fn(abatement_B)
marg_benefit <- merge(marg_benefit, demand_B, by = "row.names", all = TRUE) %>%
  select(-Row.names) %>%
  rename(demand_B = y) %>%
  arrange(abatement)

demand_C_fn <- function(x){
  slope_c*(x) + intercept_c
}

abatement_C <- seq(0,220,10)
demand_C <- demand_C_fn(abatement_C)
marg_benefit <- merge(marg_benefit, demand_C, by = "row.names", all = TRUE) %>%
  select(-Row.names) %>%
  rename(demand_C = y) %>%
  arrange(abatement)


demand_D_fn <- function(x){
  slope_d*(x) + intercept_d
}

abatement_D <- seq(0,300,10)
demand_D <- demand_D_fn(abatement_D)
marg_benefit <- merge(marg_benefit, demand_D, by = "row.names", all = TRUE) %>%
  select(-Row.names) %>%
  rename(demand_D = y) %>%
  arrange(abatement)
```

```{r, echo = FALSE}
#graph it
par(mfrow=c(2,2)) 
plot(marg_benefit$emissions_A, marg_benefit$demand_A, main = "Sector A", xlab = "Pollution Emitted (Tons)", ylab = "Marginal Benefit ($/Ton)", type = "l", col = "green")
plot(marg_benefit$emissions_B, marg_benefit$demand_B, main = "Sector B", xlab = "Pollution Emitted (Tons)", ylab = "Marginal Benefit ($/Ton)", type = "l", col = "blue")
plot(marg_benefit$emissions_C, marg_benefit$demand_C, main = "Sector C", xlab = "Pollution Emitted (Tons)", ylab = "Marginal Benefit ($/Ton)", type = "l", col = "orange")
plot(marg_benefit$emissions_D, marg_benefit$demand_D, main = "Sector D", xlab = "Pollution Emitted (Tons)", ylab = "Marginal Benefit ($/Ton)", type = "l", col = "red")

```

Demand for emission functions:
$$Demand_A = -0.58(Emissions) + 95.19 $$
$$Demand_B = -0.2(Emissions) + 49.07 $$
$$Demand_C =-0.78(Emissions) + 160.79 $$
$$Demand_D = -0.26 (Emissions)+ 87.67 $$

 - Sector C is willing to pay the most for the first unit of carbon emissions, $160.7868 per Ton. 
 
 3. Now focus on country X (which contains sectors A, B, and C). Assume there are no “co-benefits” from carbon abatement (i.e. that there are no local pollutants that are affected by carbon abatement). Suppose to meet the Paris Accord commitments, country X needs to cut all carbon emissions in half. For each of the policy options listed below, derive: (1) the total cost of meeting the target in country X, (2) the cost (or benefit) to each sector, and (3) the tax revenue generated.
  a. Cap on carbon. Each sector (A, B, and C) must cut its carbon emissions by 100 tons (thus reducing total emissions from 600 down to 300).
  b. Tax on carbon. To emit a ton of carbon in country X, you must pay a tax of $t. You will need to find the tax that accomplishes the desired reduction.
  c. Cap and trade. Each sector (A, B, C) is allocated carbon permits equal to their current emissions minus 100 (same as in (a) above), thus achieving the total reduction of 300. Then, these three sectors are allowed to trade with each other. You will need to derive the outcome of that trading.

```{r, include = FALSE}

#save y intercepts for demand curves 
demand_a_int <- marg_benefit$demand_A[marg_benefit$abatement == 180]
demand_b_int <- marg_benefit$demand_B[marg_benefit$abatement == 200]
demand_c_int <- marg_benefit$demand_C[marg_benefit$abatement == 220]
demand_d_int <- marg_benefit$demand_D[marg_benefit$abatement == 300]

marg_benefit_ag <- data.frame(marg_benefit_pollution = seq(161, 0 , -1)) %>%
  mutate(emissions_A = ifelse(
    marg_benefit_pollution <= demand_a_int, (demand_a_int - marg_benefit_pollution)/slope_a, 0 
    ), 
    emissions_B = ifelse(
    marg_benefit_pollution <= demand_b_int, (demand_b_int - marg_benefit_pollution)/slope_b, 0 
    ), 
    emissions_C = ifelse(
    marg_benefit_pollution <= demand_c_int, (demand_c_int - marg_benefit_pollution)/slope_c, 0 
    ), 
    emissions_D = ifelse(
    marg_benefit_pollution <= demand_d_int, (demand_d_int - marg_benefit_pollution)/slope_d, 0 
    )) %>%
  mutate(ag_country_X = emissions_A + emissions_B + emissions_C)

#em_A
em_A_fn <- function(price){
  -price/slope_a + demand_a_int/slope_a
  
}


em_slope_a <- -1/slope_a
em_int_a <- demand_a_int/slope_a

#em_B
em_B_fn <- function(price){
  -price/slope_b + demand_b_int/slope_b
  
}

em_slope_b <- -1/slope_b
em_int_b <- demand_b_int/slope_b


#em_C
em_C_fn <- function(price){
  -price/slope_c + demand_c_int/slope_c
  
}

em_slope_c <- -1/slope_c
em_int_c <- demand_c_int/slope_c


#em_ag 
em_slope_ag <- em_slope_a+em_slope_b+em_slope_c
em_int_ag <- em_int_a + em_int_b + em_int_c
em_ag_fn <- function(price){
  price*em_slope_ag + em_int_ag
  
}

price_slope_ag <- function(emissions){
  -em_int_ag/em_slope_ag + emissions/em_slope_ag
  
} 

tax <- price_slope_ag(300)

```

```{r}
#part a 

demand_A_fn_fixed <- function(x){
  -slope_a*(x) + demand_a_int 
}

demand_B_fn_fixed <- function(x){
  -slope_b*(x) + demand_b_int 
}

demand_C_fn_fixed <- function(x){
  -slope_c*(x) + demand_c_int 
}


polluted_units_C <- 120 #polluted units for sector C

polluted_units_B <- 100 #polluted units for sector B

polluted_units_A <- 80 #polluted units for sector A

abated_units_A <- 100 #abated units for sector A

abated_units_B <- 100 #abated units for sector B

abated_units_C <- 100 #abated units for sector C


##C NUMBERS WITHOUT TAX
pollution_benefit_C <- 120*demand_C_fn_fixed(120) + 0.5*(demand_c_int - demand_C_fn_fixed(120))*120
#13650.87 

total_benefit_C <- integrate(demand_C_fn_fixed, 0 , 220)$value

abatement_cost_C <- total_benefit_C - pollution_benefit_C
#2753.63 

#A NUMBERS WITHOUT TAX
pollution_benefit_A <- 80*demand_A_fn_fixed(80) + 0.5*(demand_a_int - demand_A_fn_fixed(80))*80
#5769.071

total_benefit_A <- integrate(demand_A_fn_fixed, 0 , 180)$value

abatement_cost_A <- total_benefit_A - pollution_benefit_A
#2019.762 

#B NUMBERS WITHOUT TAX
pollution_benefit_B <- 100*demand_B_fn_fixed(100) + 0.5*(demand_b_int - demand_B_fn_fixed(100))*100
#3912.934

total_benefit_B <- integrate(demand_B_fn_fixed, 0 , 200)$value

abatement_cost_B <- total_benefit_B - pollution_benefit_B
#1925.491 


######### Aggregated Costs and Benefits #########
abatement_cost_aggregated <- abatement_cost_A + abatement_cost_B + abatement_cost_C
#6698.883

pollution_benefit_aggregated <- pollution_benefit_A + pollution_benefit_B + pollution_benefit_C
#23332.87 
```



```{r, echo = FALSE}
par(mfrow=c(2,2)) 
plot(marg_benefit_ag$ag_country_X, marg_benefit_ag$marg_benefit_pollution, main = "Aggregate Marginal Benefits for Country X", xlab = "Pollution Emitted (Tons)", ylab = "Marginal Benefit ($/Ton)", type = "l", col = "red")
plot(marg_benefit$emissions_A, marg_benefit$demand_A, main = "Sector A", xlab = "Pollution Emitted (Tons)", ylab = "Marginal Benefit ($/Ton)", type = "l", col = "green")
plot(marg_benefit$emissions_B, marg_benefit$demand_B, main = "Sector B", xlab = "Pollution Emitted (Tons)", ylab = "Marginal Benefit ($/Ton)", type = "l", col = "blue")
plot(marg_benefit$emissions_C, marg_benefit$demand_C, main = "Sector C", xlab = "Pollution Emitted (Tons)", ylab = "Marginal Benefit ($/Ton)", type = "l", col = "orange")
```

```{r, echo = FALSE}
plot(marg_benefit_ag$ag_country_X, marg_benefit_ag$marg_benefit_pollution, main = "Aggregate Marginal Benefits for Country X", xlab = "Pollution Emitted (Tons)", ylab = "Marginal Benefit ($/Ton)", type = "l", col = "red")
lines(marg_benefit$emissions_A, marg_benefit$demand_A, main = "Sector A", xlab = "Pollution Emitted (Tons)", ylab = "Marginal Benefit ($/Ton)", type = "l", col = "green")
lines(marg_benefit$emissions_B, marg_benefit$demand_B, main = "Sector B", xlab = "Pollution Emitted (Tons)", ylab = "Marginal Benefit ($/Ton)", type = "l", col = "blue")
lines(marg_benefit$emissions_C, marg_benefit$demand_C, main = "Sector C", xlab = "Pollution Emitted (Tons)", ylab = "Marginal Benefit ($/Ton)", type = "l", col = "orange")
abline(h=tax, lty= 2)

```


```{r}
#3b 

polluted_units_C_tax <- em_C_fn(tax) #polluted units for sector C
#154.830468933185 
polluted_units_B_tax <- em_B_fn(tax) #polluted units for sector B
#48.5044240323858 
polluted_units_A_tax <- em_A_fn(tax) #polluted units for sector A
#96.6651070344293
abated_units_A_tax <- (intercept_a - tax)/ -slope_a #abated units for sector A
#83.3348929655707 
abated_units_B_tax <- (intercept_b - tax)/ -slope_b #abated units for sector B
#151.495575967614 
abated_units_C_tax <- (intercept_c - tax)/ -slope_c #abated units for sector C
#65.169531066815 

##C NUMBERS W TAX
pollution_benefit_C_tax <- polluted_units_C_tax*tax + 0.5*polluted_units_C_tax*(demand_c_int-tax)
#15499.57
total_benefit_C_tax <- integrate(demand_C_fn, 0 , 220)$value

abatement_cost_C_tax <- total_benefit_C - pollution_benefit_C
#904.9294 

#A NUMBERS WITH TAX
pollution_benefit_A_tax <- polluted_units_A_tax*tax + 0.5*polluted_units_A_tax*(demand_a_int-tax)
#6506.221 
total_benefit_A_tax <- integrate(demand_A_fn, 0 , 180)$value

abatement_cost_A_tax <- total_benefit_A - pollution_benefit_A
#1282.612 

#B NUMBERS WITH TAX
pollution_benefit_B_tax <- polluted_units_B_tax*tax + 0.5*polluted_units_B_tax*(demand_b_int-tax)
#2146.154
total_benefit_B_tax <- integrate(demand_B_fn, 0 , 200)$value

abatement_cost_B_tax <- total_benefit_B - pollution_benefit_B
#3692.271 


######### Aggregated Costs and Benefits #########
abatement_cost_aggregated_tax <- abatement_cost_A + abatement_cost_B + abatement_cost_C
#5879.812

pollution_benefit_aggregated_tax <- pollution_benefit_A + pollution_benefit_B + pollution_benefit_C
#24151.94 

tax_revenue_A <- tax*polluted_units_A_tax
#3811.175

tax_revenue_B <- tax*polluted_units_B_tax
#1912.364 

tax_revenue_C <- tax*polluted_units_C_tax
#6104.436


tax_revenue <- tax_revenue_A + tax_revenue_B + tax_revenue_C
#11827.97
```

```{r}
#3c 
#B will sell because they get the least benefit from emitting
#A and C will buy because they get more benefit from emitting
# C will buy the most because they have the highest benefit from emitting one more unit. 


```







